%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Backend Technical Lead} % Job title
    {21 Buttons} % Organization
    {Barcelona, Spain} % Location
    {Jun. 2019 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Proactively look for ways to improve the team's technical knowledge.}
        \item {Organize weekly workshops to explore trending technologies or interesting topics.}
        \item {Drastically cut down infrastructure costs by \textbf{75\%} (due to company needs) in 4 months.}
        \item {Migrate services and their data back to a \textbf{monolithic architecture} without any service interruption.}
        \item {Work in a new project called Wefan which enabled people to purchase short personalized videos from many "celebrities". Designed and implemented a \textbf{FSM} to handle the orders lifecycle (customer service review, payment, media from the celebrity, etc) integrated with \textbf{Stripe} and \textbf{Amazon SES}.}
        \item {Work in a new project called Closeapp which was a chat based application integrated with \textbf{Sendbird} and Apple's subscription system.}
        \item {Continuosly improve our codebase quality with linter tools, static typing frameworks, coverage analysis (\textbf{flake8}, \textbf{mypy}).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Job title
    {21 Buttons} % Organization
    {Barcelona, Spain} % Location
    {Apr. 2018 - Jun. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop various features in a agile environment with fully autonomous squads for a fashion social network with more than \textbf{13M users} in 10 countries.}
        \item {Design and maintain a REST API written with \textbf{Python} (Django) using \textbf{Postgres}, \textbf{ElasticSearch} and \textbf{Redis} as our main stack.}
        \item {Take part in defining an internal code architecture based on \textbf{Clean Architecture} principles.}
        \item {Use \textbf{Terraform} to manage many \textbf{AWS} services (IAM, S3, ECS, RDS, SNS/SQS, Redshift, etc).}
        \item {Improve monitoring and alerting mechanisms with technologies like \textbf{Datadog}, \textbf{Sentry}, \textbf{Grafana} and CloudWatch.}
        \item {Work towards an \textbf{event driven architecture} to achieve better interoperability between many backend services.}
        \item {Work closely with the data team to create easily managable AI services to classify and moderate content in the platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Backend Developer} % Job title
    {Imbee} % Organization
    {Barcelona, Spain} % Location
    {Jul. 2017 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrate from a PHP monolith to \textbf{Python} µservices for an instant messaging system orchestrateed with Docker Swarm.}
        \item {Develop a custom chatbot system based on finite state machines integrated with Imbee's platform.}
        \item {Write high performant async Python code for various tasks: API, message consumers, custom Prometheus metrics, data recollection, etc.}
        \item {Build and maintain \textbf{Docker Swarm} clusters, hosted in AWS, for various environments with fully automated CI/CD pipelines using \textbf{Gitlab Runners}.}
        \item {Deployed a centralized monitoring system (Grafana + Prometheus) to gather metrics from different sources: Redis, Ejabberd, AWS, docker run-time.}
        \item {Write custom \textbf{Ejabberd} modules to integrate it with \textbf{MariaDB} and \textbf{RabbitMQ}.}
        \item {Load testing, tuning EC2 instances for heavy loads (\textbf{25k+} concurrent users) and develop a high availability architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Department Internship} % Job title
    {Sallent Town Hall} % Organization
    {Sallent, Spain} % Location
    {Feb. 2017 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Management of several virtual servers (Microsoft Server).}
        \item {User login management with Active Directory.}
        \item {Network design to connect several locations of Sallent using optical fiber.}
        \item {Develop an internal web application to search employees' phone extensions. Used \textbf{Flask} + \textbf{MariaDB} with \textbf{Docker}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
